---
title: "Build and deploy a stroke prediction model using R"
date: "`r Sys.Date()`"
output: html_document
author: "Edinson Cespedes"
---

# About Data Analysis Report

This RMarkdown file contains the report of the data analysis done for the project on building and deploying a stroke prediction model in R. It contains analysis such as data exploration, summary statistics and building the prediction models. The final report was completed on `r date()`. 

**Data Description:**

According to the World Health Organization (WHO) stroke is the 2nd leading cause of death globally, responsible for approximately 11% of total deaths.

This data set is used to predict whether a patient is likely to get stroke based on the input parameters like gender, age, various diseases, and smoking status. Each row in the data provides relevant information about the patient.


# Task One: Import data and data preprocessing

getwd()
list.files()
setwd("Build-deploy-stroke-prediction-model-R")
list.files()


stroke_data <- read.csv("stroke.csv")
head(stroke_data)

str(stroke_data)
summary(stroke_data)

source("01_clean_data.R")
source("02_impute_missing.R")

## Load data and install packages

```{r}
install.packages("caret")

library(caret)

stroke_data$stroke <- as.factor(stroke_data$stroke)
levels(stroke_data$stroke)  # Deberías ver: "0" "1"

if (!requireNamespace("caret", quietly = TRUE)) {
  install.packages("caret")
}
library(caret)

source("03_transform_data.R")

sum(is.na(stroke_data$bmi))

colSums(is.na(stroke_data))


```


## Describe and explore the data

```{r}
source("04_feature_engineering.R")
source("05_eda_stroke.R")
source("06_explore_data.R")
```



# Task Two: Build prediction models

```{r}
source("02_recipe.R")
source("03_model_stroke.R")
source("04_evaluate_cv.R")
source("05_evaluate_test.R")
source("06_interpret_results.R")
```




# Task Three: Evaluate and select prediction models

```{r}
final_fit.rds
log_reg_tune.rds
rf_tune
```



# Task Four: Deploy the prediction model

```{r}
source("../3rd Part deployment/07_save_model.R")
source("../3rd Part deployment/08_app_stroke.R")
shinyApp(ui = ui, server = server)
```




# Task Five: Findings and Conclusions
conclusion_es.md
conclusion_en.md































